\section{Introduction}\label{sec:intro}

Household inflation expectations shape monetary policy
transmission. If those beliefs systematically overshoot
realized inflation after salient price signals, communication
strategies designed for rational updaters will miscalibrate.

China concentrates this problem. Food prices carry outsized
weight in the consumer basket and generate irregular swings
that dominate media coverage. The People's Bank of China
(PBoC) conducts quarterly depositor surveys in which urban
households report directional price expectations. Geopolitical
episodes, trade-policy shocks, and pandemic disruptions add
further salience bursts. Whether households update beliefs
proportionally or overweight the most recent signal
determines whether forecast errors are noise or predictable.

\citet{Bordalo2020b} formalize this distinction.
Under diagnostic expectations, agents overweight states
of the world that have become more likely in light of
recent news relative to a baseline, generating predictable
forecast-error reversals: upward revisions are followed
by negative errors once realized inflation undershoots the
revised belief. The \citet{Coibion2015} information-rigidity
framework predicts the opposite pattern at the aggregate level,
where sluggish updating produces persistent positive
autocorrelation in forecast errors. These two models yield
competing testable predictions on the sign and timing of
the revision--error link, which means the same dataset can
discriminate between them if the identification design
separates measurement from mechanism.

Existing empirical work on expectations in China documents
errors but does not cleanly separate the channel through
which those errors arise. Aggregate time-series regressions
can fit both diagnostic and rigidity interpretations depending
on control sets and sample windows. Structural VAR exercises
that define the shock of interest as the pattern to be
explained create a circularity that reviewers at top-field
journals will reject. The missing element is an external
source of variation in the salience of inflation signals
that shifts revisions without directly moving realized
inflation through a separate channel.

I address this gap with a three-layer empirical design
applied to two complementary data sources. The aggregate
layer uses the PBoC depositor survey from 2011Q1 to 2025Q3,
quantified through Carlson--Parkin inversion with explicit
treatment of uncertain responses as bound information.
The micro layer draws on seven waves of the China Family
Panel Studies (CFPS, 2010--2022), which surveys approximately
16,000 households across 25 provinces on price expectations,
income trajectories, consumption, and financial decisions.
The combination lets me test diagnostic behavior at the
national level, where the time-series variation identifies
the mechanism, and at the household level, where
cross-sectional heterogeneity pins down who overreacts and
through what margin.

The identification spine combines a reduced-form diagnostic
test with salience-IV augmentation. The workhorse is a
Newey--West regression of forecast errors on expectation
revisions, where the diagnostic-expectations hypothesis
predicts a negative coefficient: upward revisions should be
followed by downward errors as realized inflation fails to
match the overshoot. I complement this with an instrumental
variable design that uses media congestion from geopolitical
news to isolate exogenous variation in inflation salience.
I evaluate the exclusion restriction against explicit threats:
placebo outcomes that should not respond to salience shifts,
lead revisions that should not predict current errors if
anticipation contaminates the design, and permuted
instruments that should not replicate the main coefficient
in a short sample.

The core result supports the diagnostic prediction.
In OLS specifications with macro controls, forecast
revisions predict subsequent forecast errors with a negative
sign ($\hat{\beta}_1 = -2.24$, Newey--West $t = -2.0$,
$p = 0.055$, $N = 32$). The coefficient is stable across
nested control sets, ranging from $-1.66$ (bivariate)
to $-2.24$ (full controls). The salience-IV reduced form
reinforces the direction ($-0.41$), though the first stage
is admittedly weak ($F = 1.16$), making the IV estimate
suggestive rather than definitive. Anderson--Rubin
weak-IV-robust confidence intervals remain informative.
Local projections sharpen the timing: revision shocks move
forecast errors within one quarter and then attenuate, while
the realized-inflation response is smaller and fades faster,
producing a temporal asymmetry that is difficult to generate
under pure information rigidity where delayed correction
should accumulate rather than dissipate.

Heterogeneity analysis exploits both data sources.
At the aggregate level, the revision--error slope is more
negative in low-salience terciles ($\hat{\beta} = -4.04$)
and mid-salience terciles ($-3.76$) than in high-salience
terciles ($+2.24$), suggesting that the diagnostic pattern
is strongest when inflation signals compete with other
information. Interaction terms with EPU and GPR indicators
carry the predicted signs but are imprecisely estimated,
reflecting the limited power of a 32-quarter sample to
detect state dependence. At the household level, CFPS
microdata confirm diagnostic overreaction with a revision
coefficient of approximately $-0.55$ ($p < 0.001$,
$N \approx 13{,}700$ with province and wave fixed effects).
Interaction terms with education, income, and urban status
carry the predicted signs but are individually insignificant,
suggesting that overreaction is pervasive across demographic
groups rather than concentrated among particular
subpopulations.

A mechanism-competition exercise pits diagnostic overreaction
against information rigidity in the same specification.
When both the revision (diagnostic) and lagged forecast error
(rigidity) channels enter jointly, the lagged-error channel
carries a significant negative coefficient ($-0.60$,
$p = 0.005$), while the revision coefficient attenuates and
loses significance. This is consistent with both mechanisms
operating simultaneously, with information rigidity
accounting for a larger share of predictable variation in
this short sample. When state-dependent interactions are
added, the revision channel becomes more negative in
high-uncertainty periods ($-1.72$), suggesting that the
diagnostic margin activates under specific conditions
even when the unconditional horse race favors rigidity.
This evidence suggests that both channels operate in Chinese
expectation formation, with their relative importance
varying across economic states.

A Bayesian state-space model tracks time variation in the
diagnostic coefficient. The posterior path shows that
$\beta_t$ spikes during geopolitical crises (2016Q1 RMB
depreciation, 2018Q3 trade-war escalation, 2020Q2 pandemic
onset) and relaxes toward zero in calmer periods.
Convergence diagnostics (split-chain $\hat{R} < 1.05$,
ESS above 400) confirm reliable posterior inference.
An appendix BVAR with sign restrictions provides structural
consistency checks.

The final layer translates estimates into policy. I map the
diagnostic relation into a forecast-adjustment rule that
corrects raw survey expectations by the estimated
overreaction component. A rolling backtest shows that the
adjusted rule reduces MAE by 17\% and improves 68\%
interval coverage from 42\% to 67\% relative to naive
survey forecasts, providing a measurable risk metric for
when survey expectations are most likely to overstate
near-term inflation.

This paper contributes to four literatures.
To the diagnostic-expectations literature initiated by
\citet{Bordalo2018}, I provide the first household-level
test outside the United States and Europe, using a sample
where information frictions and salience shocks are
quantitatively larger than in developed-market surveys.
To the expectations-formation literature in the tradition
of \citet{Coibion2015}, I add a competing-mechanism design
that separates diagnostic from rigidity channels in the
same empirical frame rather than testing each in isolation.
To the empirical literature on Chinese macroeconomic
expectations, I move beyond reduced-form documentation of
errors toward identification-first evidence with explicit
threat evaluation. To the policy-design literature, I
demonstrate that diagnostic estimates can be translated
into a computable forecast-adjustment rule with
out-of-sample validation, rather than remaining as a
behavioral characterization without operational content.

The inference remains sample-bound. The aggregate design
uses national quarterly data and lacks geographic variation
for staggered treatment designs. The CFPS household panel
provides cross-sectional heterogeneity but observes price
expectations only every two years, limiting dynamic analysis
at the micro level. Media congestion is a plausible but not
experimentally assigned instrument. These boundaries define
where the results generalize and where future work with
province-household matched data and richer media
microstructure can extend the identification logic without
changing the mechanism definitions used here.

The paper proceeds as follows. Section~\ref{sec:literature}
positions the analysis within the diagnostic-expectations
and information-rigidity literatures and derives testable
predictions. Section~\ref{sec:data} describes the
institutional setting, the PBoC depositor survey, and the
CFPS household panel. Section~\ref{sec:measurement} details
the Carlson--Parkin quantification and CFPS expectation
construction. Section~\ref{sec:identification} presents the
salience-IV design and threat-evaluation protocol.
Section~\ref{sec:results} reports baseline estimates and
local projections. Section~\ref{sec:heterogeneity} examines
cross-sectional and state-dependent heterogeneity.
Section~\ref{sec:mechanism} competes diagnostic and
rigidity channels. Section~\ref{sec:policy} maps estimates
into a forecast-adjustment rule and reports backtests.
Section~\ref{sec:robustness} summarizes robustness and
points to appendix details. Section~\ref{sec:conclusion}
concludes.
