\section{Conceptual Framework and Related Literature}\label{sec:literature}

The diagnostic-expectations hypothesis rests on a
specific cognitive mechanism. When agents receive news
that shifts the likelihood of some state of the world,
they overweight that state in forming beliefs relative to
an objective Bayesian benchmark. \citet{Kahneman1972}
identify this as representativeness: recent or vivid
information receives disproportionate attention because
it comes to mind more readily than base rates.
\citet{Gennaioli2010} formalize this intuition in a
model where the probability of a state is inflated by a
factor that depends on how much its likelihood has
increased relative to a reference distribution. The
distortion is multiplicative: states that have become much
more likely are overweighted by more, and the degree of
overweighting is governed by a single parameter $\theta$
that indexes diagnostic intensity.

\citet{Bordalo2018} apply this framework to credit
markets and show that diagnostic beliefs generate
predictable boom-bust cycles in credit spreads.
\citet{Bordalo2020b} extend the test to macroeconomic
expectations using the Survey of Professional
Forecasters and the Michigan Survey of Consumers,
documenting that consensus forecast revisions predict
subsequent forecast errors with a negative sign across
multiple variables. Their test exploits a clean
implication of the model: if agents overreact to news,
then positive revisions should be followed by negative
forecast errors as realized outcomes fall short of inflated
beliefs. Under rational expectations, revisions and
subsequent errors are orthogonal. Under information
rigidity in the \citet{Coibion2015} tradition, revisions
and errors should be positively correlated at the
aggregate level because sluggish updaters incorporate
old news slowly, generating persistent underreaction
rather than overreaction.

\subsection{The revision--error link as a discriminating test}

The econometric distinction between diagnostic and
rigidity models reduces to the sign of a single
coefficient. Define the one-step-ahead forecast error as
$FE_{t+1} = \pi_{t+1} - \mu_t$, where $\pi_{t+1}$ is
realized inflation and $\mu_t$ is the quantified
expectation formed at time $t$. Define the revision as
$FR_t = \mu_t - \mu_{t-1}$. The diagnostic prediction is
\begin{equation}\label{eq:diagnostic_prediction}
  \E[FE_{t+1} \mid FR_t > 0] < 0,
\end{equation}
which states that upward revisions are followed by
negative forecast errors because the revision overshoots
the warranted Bayesian update. The information-rigidity
prediction, following the Coibion--Gorodnichenko
regression of forecast errors on lagged consensus
forecast changes, is
\begin{equation}\label{eq:rigidity_prediction}
  \E[FE_{t+1} \mid FE_t > 0] > 0,
\end{equation}
reflecting persistent undershoot of the full-information
rational expectation.

These predictions are not mutually exclusive in principle:
a household could simultaneously underreact to some
signals and overreact to others, depending on salience and
attention allocation. The empirical design in this paper
tests both channels in the same specification, so that
neither wins by omission of the other. What matters for
mechanism discrimination is not whether each channel
has non-zero explanatory power in isolation, but which
dominates conditional on the other and whether the
dominant channel exhibits the state dependence that its
theory predicts.

\subsection{Diagnostic expectations beyond professional forecasters}

Most empirical tests of diagnostic expectations use
professional forecaster panels, where the maintained
assumption of approximate rationality is more defensible
and where long histories enable power. \citet{Bordalo2020b}
use the SPF and Michigan Survey; subsequent work applies
similar tests to credit analysts, macroeconomic
forecasters in other countries, and equity analysts. The
extension to household surveys is less developed for
two reasons. Household expectations are noisier,
reflecting heterogeneous information sets and survey
comprehension, which inflates measurement error in
both revisions and forecast errors. And household
surveys in most countries are either qualitative
(requiring quantification through methods like
Carlson--Parkin) or available only at low frequency
with irregular panels, making the time-series dimension
short relative to the number of parameters.

These measurement challenges do not invalidate the
diagnostic test; they change the identification burden.
With noisier data, an OLS revision--error regression
will attenuate the diagnostic coefficient toward zero,
making a significant negative estimate more rather
than less informative. The Carlson--Parkin quantification
introduces a separate layer of measurement error whose
direction depends on the sensitivity parameter $\delta$
(the threshold within which respondents report ``same'').
I handle this through bound analysis: allocating uncertain
responses to pessimistic and optimistic extremes
generates lower and upper bounds on the quantified
expectation, and the diagnostic sign must hold across
bounds to be credible.

\subsection{Expectations in the Chinese context}

The Chinese institutional environment amplifies both
the diagnostic and rigidity channels. On the diagnostic
side, food-price volatility is substantially higher than
in OECD economies because pork-cycle dynamics, weather
shocks, and African Swine Fever outbreaks generate
large, sudden price movements that saturate media
coverage and conversation. When pork prices rose by
over 100\% year-on-year in late 2019, the salience of
inflation was impossible for any urban household to
ignore, regardless of whether they tracked CPI statistics.
This is exactly the environment where representativeness
should dominate base-rate reasoning: a vivid, recent
price signal that is easy to recall and hard to calibrate
against historical distributions.

On the rigidity side, the PBoC's communication
infrastructure is less developed than the Federal
Reserve's or the ECB's. Forward guidance is limited,
press conferences are infrequent, and the monetary-policy
framework has shifted multiple times between quantity-based
and price-based targets during the sample period
\citep{Chen2022}. Information asymmetry between the
central bank and households may therefore be larger in
China than in economies with more transparent communication,
which could generate sticky updating even in the absence
of cognitive biases.

The empirical question is which channel dominates when
both are present. If diagnostic overreaction is the primary
source of forecast errors, the policy implication is that
communication should counteract vivid narratives rather
than simply releasing more information. If rigidity
dominates, the implication is that more frequent and
clearer communication will reduce errors by closing the
information gap. These are different prescriptions for the
same central bank, and distinguishing between them
requires an identification strategy that separates salience
from information provision.

\subsection{Household heterogeneity and attention allocation}

Diagnostic behavior should not be uniform across households.
Attention is a scarce resource, and households with lower
education, less financial literacy, or tighter cognitive
budgets should be more susceptible to representativeness
because they rely more heavily on the most salient signal
rather than integrating multiple information sources
\citep{Lusardi2014, Reis2006}. \citet{Malmendier2016}
show that experienced inflation shapes beliefs persistently,
with stronger effects among demographics that process
statistical information less fluently. \citet{DAutume2024}
document that inflation expectations are more dispersed
among less-educated respondents in both U.S. and European
surveys.

The CFPS microdata allow a direct test of this heterogeneity
prediction. By interacting the revision--error slope with
household characteristics---education, income, urban/rural
registration, financial-asset holdings---I can test whether
diagnostic intensity is monotonically increasing in proxies
for attention constraints. This test goes beyond the
aggregate state dependence documented in the time-series
analysis, because it uses cross-sectional variation within
a given information environment rather than comparing
different macro states that may confound attention with
other time-varying factors.

\subsection{Relation to the macro-expectations literature}

The broader macroeconomic-expectations literature provides
context for interpreting the diagnostic coefficient.
\citet{Mankiw2002} show that sticky information can
replicate many features of observed inflation dynamics,
and \citet{Mankiw2003} document substantial cross-sectional
disagreement in expectations that is inconsistent with
homogeneous rational updating. \citet{Sims2003} derives
optimal attention allocation under capacity constraints,
predicting that agents attend to the most volatile or most
relevant signals rather than forming fully rational
expectations about all variables.
\citet{Mackowiak2009} extend this framework to price
setting with rational inattention. \citet{Gabaix2020}
embeds behavioral inattention into a New Keynesian model,
showing that bounded rationality in expectations can
resolve several macro puzzles including the forward-guidance
puzzle \citep{Angeletos2018} and excess sensitivity of
consumption to anticipated income changes.

This paper does not propose a new theoretical framework.
Instead, it takes the \citet{Bordalo2020b} diagnostic
model as the maintained hypothesis and asks whether the
testable predictions survive in a setting where information
frictions are larger, food-price salience is more volatile,
and institutional communication is less transparent than in
the U.S. surveys where the model was originally validated.
The CFPS household dimension adds a margin that the existing
literature has not exploited: individual-level heterogeneity
in diagnostic intensity, which can discipline the attention
parameters that theoretical models treat as free.
