\section{Measurement}\label{sec:measurement}

\subsection{Carlson--Parkin quantification}

The PBoC depositor survey reports qualitative response
shares: the fraction of respondents who expect prices to
rise ($p^{up}$), stay the same ($p^{same}$), fall
($p^{down}$), or who are uncertain ($p^{unc}$). To
construct a quantitative expectation measure, I apply
the \citet{Carlson1975} method, which assumes that
individual expected inflation rates are drawn from a
normal distribution and that each respondent reports
``up'' if their expected inflation exceeds a perception
threshold $\delta$, ``down'' if it falls below $-\delta$,
and ``same'' otherwise.

Under these assumptions, the cumulative normal at the
upper threshold equals the fraction reporting ``same'' or
``down,'' and the cumulative normal at the lower threshold
equals the fraction reporting ``down'' alone. Inverting
these two conditions yields the mean and standard deviation
of the latent distribution:
\begin{align}
  \mu_t^{CP} &= \delta \cdot
    \frac{\Phi^{-1}(1 - p_t^{up}) +
          \Phi^{-1}(p_t^{down})}
         {\Phi^{-1}(1 - p_t^{up}) -
          \Phi^{-1}(p_t^{down})}, \label{eq:cp_mean} \\
  \sigma_t^{CP} &= \frac{2\delta}
    {\Phi^{-1}(1 - p_t^{up}) -
     \Phi^{-1}(p_t^{down})}, \label{eq:cp_sd}
\end{align}
where $\Phi^{-1}$ is the standard normal quantile function
and $\delta$ is the indifference threshold, calibrated to
the sample-average realized inflation rate following
standard practice.

Two features of this mapping require explicit treatment.

\paragraph{The role of uncertain respondents.}
The ``hard to say'' response cannot be mechanically assigned
to either tail without changing the quantified expectation.
Rather than dropping uncertain respondents as noise---a
common but problematic choice that assumes
non-informativeness---I construct three measures. The
benchmark renormalizes shares by excluding uncertain
respondents ($p^{up}/(1 - p^{unc})$, etc.), which
implicitly distributes them in proportion to the
directional shares. The lower bound allocates all
uncertain respondents to the ``down'' category, producing
the most optimistic (lowest) expectation. The upper bound
allocates them to ``up,'' producing the most pessimistic
(highest) expectation. The diagnostic coefficient must
retain its sign across all three measures for the result
to be credible.

Table~\ref{tab:cp_bounds} reports the expectation series
under each allocation. The bound spread averages
approximately 0.8 percentage points and widens in quarters
where the uncertain share exceeds its median, which
coincides with high-uncertainty macro states. This
covariation between measurement precision and economic
conditions is a feature of the data, not a flaw: it
means that identification is hardest exactly where the
economic question is most interesting, and the bound
analysis makes this tension visible rather than concealing
it behind a single point estimate.

\paragraph{Sensitivity to the threshold parameter.}
The threshold $\delta$ determines the scale of quantified
expectations: higher $\delta$ stretches the distribution
and produces larger absolute values of $\mu^{CP}$. I
set $\delta$ equal to the sample-average realized CPI
inflation rate (approximately 0.5 percentage points per
quarter, annualized), following the convention that
respondents report ``same'' if they perceive inflation
within a half-point of zero. Robustness checks in
Appendix~\ref{app:data} report results under alternative
$\delta$ values (0.3, 0.7, 1.0), and the diagnostic
coefficient is stable across these choices because
$\delta$ scales both the revision and the forecast error,
leaving their ratio approximately invariant.

\subsection{CFPS household-level expectations}

The CFPS price-expectation question has a similar
qualitative structure: respondents report whether they
expect local commodity prices to rise, stay about the
same, or fall over the coming year. I apply the
Carlson--Parkin inversion at the individual level by
treating each respondent's answer as a draw from a
Bernoulli distribution over the three categories, then
aggregating within province-year cells to obtain
provincial expectation measures with sufficient
observations per cell for the normal approximation
to hold.

For household-level analysis that exploits individual
variation, I construct a simpler ordinal coding:
$\tilde{\mu}_{it} = 1$ if the respondent expects prices
to rise, $\tilde{\mu}_{it} = 0$ for ``same,'' and
$\tilde{\mu}_{it} = -1$ for ``fall.'' This ordinal measure
cannot be directly compared to the quantified PBoC
expectation in levels, but it can identify whether the
probability of overreaction (switching from ``same'' or
``down'' to ``up'' followed by realized inflation staying
flat or falling) varies with household characteristics
in the direction predicted by attention-allocation models.

I define a CFPS-specific diagnostic indicator at the
household level. For each household observed in consecutive
waves ($t-1, t$), I classify a revision as positive if
the household's price expectation moved upward (from ``same''
to ``up,'' or from ``down'' to ``same'' or ``up''). I then
check whether realized provincial CPI between wave $t$ and
wave $t+1$ fell short of the implied expectation direction.
Because CFPS waves are biennial, this test operates at a
two-year horizon rather than the quarterly horizon of the
PBoC analysis, which reduces power but tests whether
diagnostic behavior persists at longer frequencies.

\subsection{Forecast errors, revisions, and derived objects}

All derived objects in the estimation follow explicit
definitions tied to survey timing.

\paragraph{Quarterly panel (PBoC).}
The forecast revision is $FR_t = \mu_t^{CP} - \mu_{t-1}^{CP}$,
and the forecast error is $FE_{t+1} = \pi_{t+1}^{QoQ} - \mu_t^{CP}$,
where $\pi_{t+1}^{QoQ}$ is the quarter-on-quarter annualized CPI
inflation rate in the quarter following the survey.

\paragraph{Household panel (CFPS).}
The revision at the household level is
$\Delta\tilde{\mu}_{it} = \tilde{\mu}_{it} - \tilde{\mu}_{i,t-1}$,
and the forecast error is constructed using provincial
CPI inflation between wave $t$ and $t+1$ relative to the
direction implied by $\tilde{\mu}_{it}$.

These definitions ensure that the revision uses only
information available at time $t$ and that the forecast
error uses only outcomes realized after $t$, which prevents
mechanical correlation between the left-hand and right-hand
sides of the regression. The distinction between revision
and level matters because diagnostic expectations predict
that the revision (news) determines the direction of the
error, not the level of the expectation.
Table~\ref{tab:desc_extended} reports the joint
distribution of revisions and subsequent errors in the
quarterly panel, confirming that the negative association
visible in Figure~\ref{fig:revision_error_dynamics} holds
across the full distribution rather than being driven by
outlier quarters.

\input{\tabdir/desc_stats_extended}
