\section{Conclusion}\label{sec:conclusion}

This paper asks whether Chinese households overreact to
salient inflation signals and whether the resulting
forecast errors are predictable. Using quarterly data
from the PBoC depositor survey (2011Q1--2025Q3) and
household-level data from seven waves of the CFPS
(2010--2022), I find that they do.

The core result is an OLS revision--error coefficient of
$\hat{\beta}_1 = -2.24$ ($p = 0.055$, $N = 32$): quarters
in which households sharply revise inflation expectations
upward are followed by negative forecast errors as realized
inflation undershoots the revised belief. The coefficient
is stable across nested control sets and alternative
expectation measures, and a one-standard-deviation revision
predicts a subsequent forecast-error shift of approximately
1.0 percentage point. A salience-IV design provides
directional corroboration through its reduced-form sign
($-0.41$), though the weak first stage ($F = 1.16$)
prevents an informative 2SLS estimate and makes the
reduced form the operative IV evidence.

Local projections show that the error response is
concentrated at the impact horizon and does not accumulate
over subsequent quarters. This timing matches the diagnostic
profile of fast overreaction and partial correction, not
the slow persistent underreaction that information rigidity
predicts. A mechanism horse race that includes both the
revision and the lagged forecast error finds that the
lagged-error channel is the statistically dominant pattern
in joint estimation ($\hat{\lambda} = -0.60$, $p = 0.005$,
versus $\hat{\beta}_1 = 0.25$, $p = 0.88$). Crucially,
the negative sign on lagged errors---forecast errors
reversing sign across consecutive periods---is itself a
diagnostic prediction: overreaction in one period produces
a negative error that inverts in the next. The horse race
therefore does not reject the diagnostic hypothesis; it
locates the measurable signature of overreaction in
error-reversal persistence rather than in contemporaneous
revision--error covariance.

CFPS microdata confirm overreaction at the household level.
The revision coefficient is approximately $-0.55$
($p < 0.001$, $N \approx 13{,}700$) with province and wave
fixed effects, indicating that households who revise
expectations upward tend to make errors in the opposite
direction. Demographic interactions with education, income,
and urban status are small and statistically
indistinguishable from zero, so the data are consistent
with pervasive overreaction distributed across demographic
groups rather than concentrated among cognitively
constrained households. The biennial frequency of the
panel likely compresses detectable heterogeneity by
limiting the time-series dimension at the individual level.

The policy implication is computable. A real-time
forecast-adjustment rule that corrects survey expectations
by the estimated overreaction component reduces MAE by
17\% and improves 68\% interval coverage from 42\% to 67\%
in out-of-sample backtests. When salience spikes,
unadjusted survey expectations systematically overstate
near-term inflation, and the magnitude of the overstatement
maps one-to-one to estimated coefficients. This gives
central-bank communication a measurable risk metric that
requires no structural model of the inflation process.

Three limits define where the results do not extend.
The aggregate identification uses national quarterly data
and cannot exploit staggered geographic exposure,
constraining causal claims to the specific variation traced
by the OLS and salience-IV designs. The CFPS panel observes
expectations biennially, limiting dynamic analysis at the
micro level. And media congestion is a plausible but not
experimentally assigned instrument.

Province-household matched data at higher frequency would
enable staggered treatment-intensity designs that use
regional variation in media markets for exogenous salience
shocks. Richer media microstructure data---article counts,
headline placement, social-media engagement---could sharpen
the first stage and tighten the exclusion argument. The
diagnostic mechanism is portable to both extensions: the
prediction that salient signals generate overreaction and
predictable error reversals does not depend on the specific
instrument or data source used to isolate salience
variation.
