\section{Bayesian State-Space Model}\label{app:ssm}

This appendix details the Bayesian state-space model (SSM)
that estimates time variation in the diagnostic coefficient.
The SSM serves a diagnostic function: it tracks how
$\beta_t$ evolves over the sample and verifies that the
frequentist baseline results are not driven by parameter
instability or by specific subperiods. The SSM does not
provide independent causal identification; its role is
to complement the salience-IV design by showing that
the diagnostic relation varies in economically
interpretable ways over time.

\subsection{Model specification}

The measurement equation links observable forecast errors
to revisions and controls with a time-varying coefficient:
\begin{align}
  FE_t &= \alpha + \beta_t FR_t + \gamma' Z_t
    + \varepsilon_t, \qquad
    \varepsilon_t \sim \mathcal{N}(0, R),
    \label{eq:ssm_measurement} \\
  \beta_t &= \beta_{t-1} + d' X_t + u_t, \qquad
    u_t \sim \mathcal{N}(0, Q),
    \label{eq:ssm_state}
\end{align}
where $Z_t$ contains macro controls (food CPI, M2 growth,
PPI inflation), $X_t$ contains the EPU and GPR indices
as potential drivers of time variation, and $R$, $Q$ are
scalar variances governing measurement noise and state
innovation, respectively.

The state equation allows $\beta_t$ to evolve as a random
walk with drift terms driven by observable uncertainty
proxies. If $d = 0$, the model reduces to a pure random
walk in diagnostic intensity. If $Q = 0$, the model
collapses to a fixed-coefficient regression. The data
inform the relative importance of drift, external drivers,
and noise through the posterior distributions of $d$, $Q$,
and $R$.

\subsection{Prior specification}

I use conjugate priors that encode mild beliefs about
parameter ranges while letting the data dominate:
\begin{align*}
  \beta_0 &\sim \mathcal{N}(-0.5, 0.5^2), \\
  \alpha, \gamma &\sim \mathcal{N}(0, 10^2), \\
  d &\sim \mathcal{N}(0, 0.2^2), \\
  R &\sim \text{Inv-Gamma}(3, 0.001), \\
  Q &\sim \text{Inv-Gamma}(3, 0.001).
\end{align*}

The prior for $\beta_0$ is centered at $-0.5$,
reflecting the OLS point estimate, with a standard
deviation of $0.5$ that allows the posterior to range
from approximately $-1.5$ to $+0.5$. The prior for $d$
(the drift coefficients on EPU and GPR) is tighter,
reflecting the expectation that external drivers explain
only modest variation in $\beta_t$ beyond the random-walk
component. The Inverse-Gamma priors on variances are
weakly informative with 3 degrees of freedom.

\subsection{Estimation}

Posterior inference uses a Gibbs sampler that alternates
between three blocks:
\begin{enumerate}
  \item \textbf{State path:} Sample $\{\beta_t\}_{t=1}^T$
    conditional on parameters via Forward Filtering
    Backward Sampling \citep{CarterKohn1994}.
  \item \textbf{Regression coefficients:} Sample
    $(\alpha, \gamma, d)$ from their conditional normal
    posteriors.
  \item \textbf{Variances:} Sample $R$ and $Q$ from
    their conditional Inverse-Gamma posteriors.
\end{enumerate}

I run 20,000 iterations, discard 5,000 as burn-in, and
thin every 10th draw to yield 1,500 posterior samples.
Three independent chains from dispersed starting values
are used for convergence assessment.

\subsection{Convergence diagnostics}

Table~\ref{tab:mcmc_diagnostics} reports convergence
statistics. Geweke $Z$-statistics are within $\pm 1.5$
for all parameters, with $p$-values above 0.05. Gelman--Rubin
$\hat{R}$ statistics range from 0.9999 to 1.0015, well
below the 1.05 threshold. Effective sample sizes (ESS)
range from 411 ($Q$) to 2,665 ($\alpha$), all above the
400 threshold for reliable inference.

\input{\tabdir/mcmc_diagnostics}

\subsection{Posterior results}

Table~\ref{tab:ssm_posterior_params} reports posterior
means and 90\% credible intervals for measurement-equation
parameters. The intercept $\hat{\alpha} = -0.315$
($[-0.446, -0.188]$) confirms a systematic upward bias
in expectations even after conditioning on revisions.
Food CPI and M2 growth carry marginally significant
negative coefficients, consistent with households
overreacting to food-price and money-supply signals
beyond the diagnostic channel.

The state-equation drift coefficients are
$\hat{d}_{EPU} = +0.067$ ($[-0.15, +0.29]$) and
$\hat{d}_{GPR} = -0.093$ ($[-0.38, +0.19]$). Neither
is precisely estimated, which means that the linear
association between uncertainty indices and $\beta_t$
is directionally intuitive but statistically fragile.
The positive sign on EPU (higher policy uncertainty
associated with less negative $\beta_t$) and negative
sign on GPR (geopolitical risk associated with more
negative $\beta_t$) suggest that different types of
uncertainty may affect diagnostic behavior through
different channels, but the wide intervals caution
against over-interpretation.

\input{\tabdir/ssm_posterior_params}

\subsection{Prior sensitivity}

Table~\ref{tab:prior_sensitivity} reports posterior
results under three prior specifications: baseline
(as above), loose ($\sigma_{\beta_0} = 1.0$,
$\sigma_d = 0.5$), and tight ($\sigma_{\beta_0} = 0.25$,
$\sigma_d = 0.1$). The sign of $\beta_t$ is negative in
all specifications, and the posterior mean varies by less
than 15\% across priors. The loose prior widens credible
intervals without changing the qualitative conclusion,
while the tight prior shrinks intervals without
eliminating the negative sign. This stability confirms
that the diagnostic state is identified by data
information rather than prior dogma.

\input{\tabdir/prior_sensitivity}

\subsection{Model comparison}

Table~\ref{tab:model_comp} reports information
criteria across four specifications: frequentist OLS
with fixed $\beta$, Bayesian SSM with fixed $\beta$,
TVP-SSM without drift, and full TVP-SSM with EPU/GPR
drivers. Both TVP models achieve substantially higher
log-likelihoods than fixed-$\beta$ alternatives
($-26.9$ and $-25.2$ versus $-35.1$), confirming that
time variation in diagnostic intensity is empirically
warranted.

\input{\tabdir/model_comparison}
