\section{Data Construction Details}\label{app:data}

\subsection{PBoC depositor survey processing}

The PBoC publishes quarterly survey reports as PDF
documents in Chinese. I extract response shares from
68 reports covering 2010Q4 through 2025Q3 using a
combination of PDF parsing and manual verification.
Each report contains the fraction of respondents selecting
``prices will rise,'' ``prices will stay the same,''
``prices will fall,'' and ``hard to say.'' These shares
are stored in
\texttt{data/intermediate/pboc\_depositor\_survey\_quarterly.csv}.

The Carlson--Parkin quantification
(Section~\ref{sec:measurement}) is implemented in
\texttt{src/05\_carlson\_parkin\_quantify.R}. The script
outputs three expectation series (benchmark, lower bound,
upper bound) and a cross-validated $\delta$ parameter.
Intermediate outputs are stored in
\texttt{data/intermediate/pboc\_expected\_inflation\_cp.csv}.

\subsection{Macroeconomic data}

NBS data are downloaded from the National Bureau of
Statistics official database using the EasyQuery API
(\texttt{src/04\_download\_nbs\_easyquery.py}). Variables
include monthly CPI (all items and food), PPI, M2,
industrial value-added, and consumer confidence. Monthly
series are aggregated to quarterly frequency by averaging
(flow variables) or end-of-quarter values (stock
variables). The processed quarterly panel is stored in
\texttt{data/processed/panel\_quarterly.csv}.

The EPU index for China is sourced from the
\citet{Baker2016} website (\texttt{src/01\_download\_gpr.py}
and \texttt{src/02\_download\_epu.py}). The GPR index
is from \citet{Caldara2022}. Both are available at
monthly frequency and averaged to quarters.

\subsection{CFPS data construction}

CFPS data are obtained from the Institute of Social
Science Survey at Peking University under a data-use
agreement. Seven waves (2010, 2012, 2014, 2016, 2018,
2020, 2022) are stored as Stata .dta files in
\texttt{data/raw/CFPS/}. The processing script
(\texttt{src/12\_build\_cfps\_panel.R}) performs the
following steps:

\begin{enumerate}
  \item \textbf{Variable extraction:} From each wave's
    adult/person module, extract price-expectation
    responses, demographic variables (age, education years,
    gender, hukou status), income, and province identifiers.
  \item \textbf{Panel linkage:} Use the CFPS cross-year
    identifier (\texttt{ecfps2022crossyear\_202601.dta})
    to link individuals across waves, enabling revision
    construction.
  \item \textbf{Expectation coding:} Code price
    expectations as $+1$ (rise), $0$ (same), $-1$ (fall).
    ``Don't know'' responses are kept as a separate
    category for the uncertainty analysis.
  \item \textbf{Provincial CPI merge:} Match each
    household to its province's CPI inflation between
    waves to construct the household-level forecast-error
    proxy.
  \item \textbf{Sample restrictions:} Restrict to adults
    aged 18--70 with non-missing price expectations in
    at least two consecutive waves.
\end{enumerate}

The output is a household-wave panel stored in
\texttt{data/processed/cfps\_panel.csv} with approximately
80,000 household-wave observations.

\subsection{Variable definitions}

Table~\ref{tab:variable_dict} provides a comprehensive
variable dictionary. All variables, units, transformations,
and source scripts are documented.

\input{\tabdir/variable_dict}

\subsection{Carlson--Parkin threshold sensitivity}

Table~\ref{tab:delta_sensitivity} reports the diagnostic
coefficient under alternative perception thresholds
$\delta \in \{0.3, 0.5, 0.7, 1.0\}$. The baseline
uses $\delta = 0.5$, equal to the sample-average
quarterly annualized CPI inflation rate. The sign of
$\beta_1$ is negative across all thresholds, and the
magnitude ranges from $-0.44$ ($\delta = 0.3$) to $-0.57$
($\delta = 1.0$). The insensitivity reflects the fact
that $\delta$ scales both the revision and the forecast
error, leaving their ratio approximately invariant.

\input{\tabdir/delta_sensitivity}
