\documentclass[12pt]{article}

% --- Page layout ---
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{setspace}
\setstretch{1.5}
\setlength{\parindent}{1.5em}
\setlength{\parskip}{0.3em}

% --- CJK support (XeLaTeX) ---
\usepackage{fontspec}
\usepackage{xeCJK}
\setCJKmainfont{STSong}
\setCJKsansfont{SimHei}
\setCJKmonofont{FangSong}

% --- Math and symbols ---
\usepackage{amsmath, amssymb, amsthm}

% --- Tables ---
\usepackage{booktabs, threeparttable, tabularx, multirow, array, lscape}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

% --- Colors ---
\usepackage[dvipsnames]{xcolor}

% --- Figures ---
\usepackage{graphicx, subcaption}
\graphicspath{{../outputs/figures/}}

% --- Bibliography (biblatex + biber) ---
% chicago-authordate approximates AER style (author-year, no label)
% natbib=true lets \citet / \citep work throughout
\usepackage[backend=biber,
            style=chicago-authordate,
            natbib=true,
            uniquename=false,
            uniquelist=false]{biblatex}
\addbibresource{references.bib}

% --- Hyperlinks (load after biblatex) ---
\usepackage[colorlinks=true, citecolor=blue!60!black,
            linkcolor=blue!60!black, urlcolor=blue!60!black]{hyperref}
\usepackage{cleveref}

% --- Formatting ---
\usepackage{float}
\usepackage{caption}
\captionsetup{font=small, labelfont=bf}
\usepackage{enumitem}
\setlist{nosep, leftmargin=*}

% --- Custom commands ---
\newcommand{\tabdir}{../outputs/tables}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\iid}{\stackrel{\mathrm{iid}}{\sim}}
\DeclareMathOperator*{\argmax}{arg\,max}

% --- Title ---
\title{Diagnostic Inflation Expectations in China: \\
Salience, Overreaction, and the Limits of Rational Updating\thanks{I thank
[advisors] for guidance and [seminar participants] for comments.
All errors are my own. Replication code and data documentation
are available at [URL].}}
\author{Jingle Fu\thanks{Department of Economics,
Beijing Foreign Studies University.
Email: \href{mailto:jinglefu@bfsu.edu.cn}{jinglefu@bfsu.edu.cn}}}
\date{March 2026}

\begin{document}

\maketitle
\thispagestyle{empty}

\begin{abstract}
\noindent
Do Chinese households overreact to salient inflation signals?
I construct a quarterly panel from the People's Bank of China
depositor survey (2011Q1--2025Q3) and complement it with
seven waves of the China Family Panel Studies to test the
diagnostic-expectations hypothesis at both aggregate and
household levels. A salience-IV design, where media congestion
instruments inflation salience, traces a testable chain:
salience shifts expectation revisions, and revisions predict
subsequent forecast errors with a negative sign
($\hat{\beta} = -2.24$, $p = 0.055$, $N = 32$),
consistent with diagnostic overreaction. Local projections
show that revision shocks move forecast errors within one
quarter and then attenuate. A mechanism-competition design
reveals that both diagnostic and information-rigidity
channels carry explanatory power, with the diagnostic
margin activating more strongly during high-uncertainty
episodes. Heterogeneity analysis using CFPS microdata
shows that forecast errors conditional on revisions are
larger among less-educated, lower-income, and rural
households, consistent with attention-allocation models.
A Bayesian state-space model tracks time variation in the
diagnostic coefficient, which intensifies during geopolitical
crises and pandemic onset. Translating these estimates into
a real-time forecast-adjustment rule improves out-of-sample
MAE by 17\% and interval coverage from 42\% to 67\%
relative to naive survey forecasts.
The evidence supports diagnostic overreaction as one
operative channel in Chinese household expectation formation,
while external validity remains bounded by national
aggregation and short-horizon survey design.
\\[0.5em]
\textbf{JEL Codes:} D84, E31, E71, G41 \\
\textbf{Keywords:} Diagnostic expectations, inflation expectations,
household surveys, China, salience, Bayesian state-space
\end{abstract}

\newpage
\setcounter{page}{1}

% --- Main text ---
\input{sections/01_introduction}
\input{sections/02_literature}
\input{sections/03_institutional_data}
\input{sections/04_measurement}
\input{sections/05_identification}
\input{sections/06_baseline_results}
\input{sections/07_heterogeneity}
\input{sections/08_mechanism}
\input{sections/09_policy}
\input{sections/10_robustness}
\input{sections/11_conclusion}

% --- Appendix ---
\newpage
\appendix
\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}}
\renewcommand{\thefigure}{A\arabic{figure}}

\input{sections/A1_bayesian_ssm}
\input{sections/A2_bvar}
\input{sections/A3_data_construction}
\input{sections/A4_additional_robustness}

% --- Bibliography ---
\newpage
\printbibliography[title={References}]

\end{document}
